### 2019-01-01 index.Rmd
spellcheck

## Quick Start
If the `sf` package is already installed, the development version of `areal` can be accessed from Github with `remotes`:

>>>>

## Quick Start
If the `sf` package is already installed, the easiest way to get `areal` is to install it from CRAN:

``` r
install.packages("areal")
```

Alternatively, the development version of `areal` can be accessed from GitHub with `remotes`:
